The evolution of gene expression in the term placenta of viviparous mammals

### 2016-02-03 manuscript/manuscript.Rnw
update the abstract

  \parttitle{Results} We profiled the term placenta by using Illumina
  RNA-Seq technology to sequence the transcriptomes of
  \Sexpr{star.logs[,length(unique(species))]} species of therian (i.e.
  marsupials and “placental”) mammals.

  \parttitle{Conclusions}

>>>>

  \parttitle{Results} We measured the expression profiles of the term
  placenta of \Sexpr{star.logs[,length(unique(species))]} species of
  therian (i.e. marsupials and “placental”) mammals using RNA-Seq. We
  identified multiple genes and transcripts which are differentially
  expressed across lineages including prolactin, relaxin, and
  galectins, as well as identifying the non-housekeeping genes which
  are core to placenta function (such as components of annexin
  complexes) in all \Sexpr{star.logs[,length(unique(species))]}
  species studied.

  \parttitle{Conclusions} While there are multiple non-housekeeping
  genes which are highly expressed in all placentas examined and are
  likely to be involved in the basic functions of the mammalian
  placenta, we see incredible lineage-specific diversity in the
  expression and expansion of many genes. These lineage-specific genes
  are likely to play a role in the anatomical variability of the
  placenta and may also be implicated in important \human placental
  disorders such as pre-eclampsia.
